### 2011-12-02 docs/visualization/visualization.tex
add particle count and processor number
add python_plotfile info

\hline

@@

\hline

@@

>>>>

%\hline

@@

%\hline
{\tt particle\_count}  & number of particles in a cell & {\tt use\_particles} \\
%\hline
{\tt processor\_number} & processor number containing the cell's data & {\tt plot\_processors} \\

@@

\section{Visualizing with {\tt data\_processing} scripts}

{\tt data\_processing/python\_plotfile} provide a simple commandline tool for doing 
visualizations of 2-d BoxLib plotfiles.  The main driver
is written in python and uses a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On
a machine running Fedora linux, you can install these packages via
\begin{verbatim}
yum install python-matplotlib f2py
\end{verbatim}

The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.  A simple plot can be made via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``tfromp'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.
